---
title: "Impact"
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
source("common_code.R")
```

The following questions were asked in regards to the impact of Basic Needs programs and services on students lives. Students were asked to evaluate how they feel these programs have benefited them both academically and non-academically, as well as barriers/reasons in regards to why they are not using certain programs. This includes programs such as CalFresh, Food Pantries, Medi-Cal (also known as Medi-Cade in the United States), and Emergency Housing Services.


## CalFresh EBT

*Note: for the first graph on EBT application we have `r print_n_reporting("q47")` And for the second graph on how many people are fed we have `r print_n_reporting("fed_through_EBT")`*

```{r}
#| fig-width: 5
p1 <- plot_frq(bns$q47, wrap.title = 40, ylim=c(0,500), wrap.labels = 15, 
               title="Did you apply for CalFresh EBT as an individual or with other people in your household?") +
  xlab('')
p2 <- plot_frq(bns$fed_through_EBT, wrap.title = 40, title="How many people in the household are regularly fed through your CalFresh EBT card?") + xlab('')

p1
p2
rm(p1,p2)
```

Looking at the above graphs, the majority of people apply for CalFresh EBT as an individual (`r unname(table(bns$q47)['As an individual'])` people) while only `r unname(table(bns$q47)['With other people in my household'])` people applied with other people in their household. Similarly, the majority of people claimed only `r names(sort(table(bns$fed_through_EBT), decreasing = TRUE))[1]` person is fed through the EBT card (`r unname(sort(table(bns$fed_through_EBT), decreasing = TRUE))[1]` people). `r unname(sort(table(bns$fed_through_EBT), decreasing = TRUE))[2]` people claim to feed `r names(sort(table(bns$fed_through_EBT), decreasing = TRUE))[2]` people through the EBT card, and only a small amount of people claim to feed 5 or more people through the EBT card.

<br>

### Monthly CalFresh Money

**How much money do you receive from CalFresh each month? `r print_n_reporting("q49_1")`**

```{r}
#| fig-width: 7

gghistogram(bns, x = "q49_1", add = "mean", fill = plot_color, alpha = 1) + xlab("Monthly EBT Received ($)") + ylab("Frequency")


#is $1500 a feasible response?
```

The average amount of money received per household using CalFresh (denoted by the dotted line) is \$`r round(mean(bns$q49_1, na.rm=TRUE),2)`, while the median is \$`r round(median(bns$q49_1, na.rm=TRUE),2)`. The values range from \$`r min(bns$q49_1, na.rm=TRUE)` to \$`r max(bns$q49_1, na.rm=TRUE)`. The majority of households who do receive these benefits seems to be getting around \$250 or less per month.

### Household Size Breakdown

Below is a breakdown of the average monthly allowance received from CalFresh based on household size.

```{r}
#| fig-width: 6.5
tmp <- bns %>% group_by(fed_through_EBT) %>% 
  summarise(avg = round(mean(q49_1, na.rm=TRUE),2)) %>% 
  na.omit() %>% mutate(HH.avg = round(avg/fed_through_EBT, 2),
                       fed_through_EBT = as.character(fed_through_EBT),
                       avg = paste0("$", format(avg, nsmall=2)))

tmp[9,] <- list("", "Total Average", round(mean(tmp$HH.avg),2))
tmp <- tmp %>% mutate(HH.avg = paste0("$", format(HH.avg, nsmall=2)))
colnames(tmp) <- c("Household Size", "Household Average", "Per Person Average")

tmp %>% kable() %>% kable_styling(bootstrap_options = "striped") %>%
  row_spec(9, bold=TRUE)
```

Looking at the above table, the general pattern seems to be that as household size increases so does the monthly average assistance from CalFresh. The household average was divided by the household size to find the "per person average" for CalFresh assistance. From taking the average of these values, we can see that a person on CalFresh receives an average monthly assistance of `r tmp[9,3]`.

### Is This Enough?

*Note: for the first graph on if the allowance is enough we have `r print_n_reporting("q50")` And for the second graph on when people run out we have `r print_n_reporting("q51")`*

```{r}
#| fig-width: 6
p1 <- plot_frq(bns$q50, ylim=c(0,200), title="I feel that the amount that is added to my CalFresh EBT card each month is enough money to provide healthy food for the month.") + xlab('')
p2 <- plot_frq(bns$q51, ylim=c(0, 210), wrap.labels = 12, title="When do you typically use up the balance on your CalFresh EBT card?") + xlab('')

p1
p2
rm(p1,p2)
```

Of the people who do receive money from CalFresh, `r unname(table(bns$q50)['Agree']) + unname(table(bns$q50)['Strongly agree'])` of them agree that it is enough money to provide healthy food for a month and `r unname(table(bns$q50)['Disagree']) + unname(table(bns$q50)['Strongly disagree'])` of them feel that it is not enough. People typically run out of CalFresh money in the first week (`r unname(table(bns$q51)['First week after receiving benefits'])` people), the second week (`r unname(table(bns$q51)['Second week after receiving benefits'])` people) or the third week (`r unname(table(bns$q51)['Third week after receiving benefits'])` people). A smaller minority run out within the fourth week or do not use up all their monthly balance.

<br>

## CalFresh Benefits

**While you received CalFresh benefits:**

```{r}
#| fig-height: 8
#| fig-width: 8.5
questions <- bns %>% select(starts_with("q52_"))
names(questions) <- c('I worked fewer hours each week in a PAID position.',
                      'I had more time to do an UNPAID internship or volunteer work.',
                      'I had more money to pay for bills (rent, utility bills, clothes, etc.).',
                      'I had more money for entertainment and social activities.',
                      'I shopped more frequently at the farmers market.',
                      'I had learned more about healthier foods.',
                      'I purchased healthier foods.',
                      'I cooked more frequently at home.',
                      'I consumed a healthier diet.',
                      'I consumed less fast food.',
                      'I consumed fewer processed foods.',
                      'I consumed fewer sugar-sweetened beverages like soda and energy drinks.',
                      'I consumed less alcohol or fewer alcoholic beverages.',
                      'I concentrated more in class(es).',
                      'My grades had improved.',
                      'My grades had decreased.',
                      'I kept up with course materials..',
                      'I had more time to go to my professors office hours and tutoring services when needed.',
                      'I had more time to attend all classes as they are scheduled.',
                      'I had more time to go on field trips or internships.',
                      'My sleep quality had improved.',
                      'My stress/anxiety level had decreased.')
plot_likert(questions[1:11],
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")

plot_likert(questions[12:22],
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

## CalFresh Barriers

**What are the reasons you do not have CalFresh or have never used CalFresh? (Select all that apply).**

```{r}
question <- "calfresh_barrier"

qlabel <- c('No time to complete the application/ application is too long.', 
'The application is too difficult.', 
'The CalFresh outreach team on campus was not helpful or supportive during my application process.',
'The staff in my local county social services office were not helpful or supportive during my application process.', "It's too difficult to get my verification documents.",
'No time to call or go to the local social services office for my CalFresh interview.',
'I feel other students need CalFresh more than I do.', 
'No transportation to CalFresh office or social services office.',
'I do not think I am eligible.', 
"I have heard that it's not worth my time because I won't be eligible or I won't receive much money.", 
'My family or household does not want to apply for CalFresh.', 
'I am embarrassed or ashamed to apply for CalFresh.', 
"I don't believe in social services like CalFresh, WIC, or Welfare.",
"I don't need CalFresh.", 'Other (Please specify).', 
'I feel uncomfortable receiving help with basic needs, like food.', 
'I would think less of myself if I applied for CalFresh.',
"I don't wan't my friends to find out I'm receiving food assistance.", 
'My friends and peers would think less of me if I apply for CalFresh.')




cf_barrier_vars <- prep_binary_vars(question, qlabel) ## Issues here



# Plot table of Percentages
cf_barrier_vars %>%
select(Measure = xlab, "Yes (%)" = pct_lab) %>%
kable() %>% kable_styling(bootstrap_options = "striped") %>% column_spec(2, width='3.5cm')
```

## Food Pantry Use

**How often do you normally use the food pantry or if you are not currently using it, how often did you use it? `r print_n_reporting("q54")`**

```{r}
#| fig-height: 3.5
plot_frq(bns$q54, wrap.labels = 15) + xlab('Food Pantry Use Frequency') + ylab("Frequency")
```

When people use the food pantry, the majority do not use it every week (`r unname(sort(table(bns$q54), decreasing = TRUE)['Not every week'])` people). `r unname(sort(table(bns$q54), decreasing = TRUE)['About once a week'])` people claim to use it about once a week, `r unname(sort(table(bns$q54), decreasing = TRUE)['More than once a week'])` people use it more than once a week, and `r unname(sort(table(bns$q54), decreasing = TRUE)['Other (Please specify):'])` people claim other uses.

# Impact of Pantry

**For the following questions, please choose how much you agree or disagree with the impact campus food pantries has or had on your life. While I utilized campus food pantry/pantries:**

```{r}
#| fig-height: 8
#| fig-width: 8.5
questions <- bns %>% select(starts_with("q55_"))
names(questions) <- c('I worked fewer hours each week in a PAID position.',
                      'I had more time to do an UNPAID internship or volunteer work.',
                      'I had more money to pay for bills (rent, utility bills, clothes, etc.).',
                      'I had more money for entertainment and social activities.',
                      'I shopped more frequently at the farmers market.',
                      'I had learned more about healthier foods.',
                      'I purchased healthier foods.',
                      'I cooked more frequently at home.',
                      'I consumed a healthier diet.',
                      'I consumed less fast food.',
                      'I consumed fewer processed foods.',
                      'I consumed fewer sugar-sweetened beverages like soda and energy drinks.',
                      'I consumed less alcohol or fewer alcoholic beverages.',
                      'I concentrated more in class(es).',
                      'My grades had improved.',
                      'My grades had decreased.',
                      'I kept up with course materials.',
                      'I had more time to go to my professors office hours and tutoring services when needed.',
                      'I had more time to attend all classes as they are scheduled.',
                      'I had more time to go on field trips or internships.',
                      'My sleep quality had improved.',
                      'My stress/anxiety level had decreased.')
plot_likert(questions[1:11],
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")

plot_likert(questions[12:22],
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

### Reasons Not Using Food Pantries

**What are the reasons for you to not go to campus food pantries? (Select all that apply).**

```{r}
 question <- "no_pantry"
 qlabel <- c("My family doesn't want me to go to campus food pantries or local food banks.",
             'I am embarrassed or scared to go to the campus food pantries or local food banks.',
             'I do not believe in using campus food pantries or local food banks.',
             "Inconvenient to access due to lack of transportation or out-of-the way location.",
             'Inconvenient times of operation/limited pantry hours.',
             'I feel other students need the food more than I do.',
             'I am not aware of any campus food pantries or local food banks.',
             'There are no food pantries close to campus or my residence.',
             'Other', 
             "I don't need to use campus food pantries.", 
             'I feel uncomfortable about receiving help with basic needs, like food.',
             'I would think less of myself If I went to campus food pantries or local food banks.',
             "I don't want my friends to find out I go to campus food pantries or local food banks.",
             'My friends and peers would think less of me if I went to campus table(food pantries or local food banks.')
 
 pantry_vars <- prep_binary_vars(question, qlabel)

# Plot table of Percentages
 pantry_vars %>% 
   select(Measure = xlab, "Yes (%)" = pct_lab) %>% 
   kable() %>% kable_styling(bootstrap_options = "striped")
```

## Medi-Cal

**Knowing that you have Medi-Cal:**

```{r}
#| fig-width: 8.5
questions <- bns %>% select(starts_with("q59_"))
names(questions) <- c("My mental health has improved.",
                      "My physical health has improved.",
                      "My sleep quality had improved.",
                      "My stress/anxiety level had decreased.")
                      

plot_likert(questions,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

### Reasons Not Using Medi-Cal

**What are the reasons you do not have Medi-Cal or have never used Medi-Cal? (Select all that apply).**

```{r}
 question <- "no_medical"
 qlabel <- c("I don’t need MediCal.",
             "I do not know what MediCal is or I think I already have health insurance.",
             "I only need medical services at the student health center associated with my campus.",
             "No time to complete the MediCal application/MediCal application is too long.",
             "The MediCal application is too difficult to complete.",
             "I do not think I am eligible for MediCal.",
             "I have heard from other students that it is not worth my time because I wont be eligible.",
             "My family or household does not want me to apply for MediCal.",
             "I am embarrassed or ashamed to apply for MediCal.",
             "I don’t believe in social services like MediCal, CalFresh, WIC, or Welfare/Cash Aid.",
             "Other",
             "I feel uncomfortable about receiving help with basic needs, like food.",
             "I would think less of myself If I went to campus food pantries or local food banks.",
             "I don't want my friends to find out I go to campus food pantries or local food banks.",
             "My friends and peers would think less of me if I went to campus table(food pantries or local food banks.")
 
 medical_vars <- prep_binary_vars(question, qlabel)
 
 # Plot table of Percentages
 medical_vars %>% 
   select(Measure = xlab, "Yes (%)" = pct_lab) %>% 
   kable() %>% kable_styling(bootstrap_options = "striped")
```

## Emergency Housing Services (EHS)

**While you received Emergency Housing Services:**

```{r}
#| fig-height: 8
#| fig-width: 8.5
questions <- bns %>% select(starts_with("q62_"))
names(questions) <- c('I concentrated more in class(es).',
                      'My grades had improved.',
                      'My grades had decreased.',
                      'I kept up course materials.',
                      'I had more time to go to my professors’ office hours and tutoring services when needed.',
                      'I had more time to attend all classes as they are scheduled.',
                      'I had more time to go on field trips or internships.',
                      'My sleep quality had improved.',
                      'My stress/anxiety level had decreased.',
                      'I’m less concerned about housing issues.',
                      'I felt more confident in my ability to maintain healthy relationships.')

plot_likert(questions,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

### Reasons Not Using EHS

**What are the reasons you do not have Emergency Housing Services or have never used Emergency Housing Services?**

```{r}
 question <- "no_ehs"
 qlabel <- c("I don’t need Emergency Housing Services",
             "I was not aware that my campus had Emergency Housing Services like grants and housing placements in an emergency.",
             "No time to complete the Emergency Housing application or contact the Emergency Housing Staff.",
             "The Emergency Housing Services application is too difficult to complete.",
             "The emergency housing grant/money is not enough to support what I need, so not worth my time to apply for it.",
             "I am embarrassed or ashamed to apply for Emergency Housing Services.",
             "I do not believe in social services like Emergency Housing Services, MediCal, CalFresh, or Welfare/Cash Aid.",
             "Other", 
             "I feel uncomfortable about receiving help with basic needs, like housing.",
             "I would think less of myself if I applied for Emergency Housing Services.",
             "I don't want my friends to find out that I applied for emergency housing services.",
             "My friends and peers would think less of me if I applied for emergency housing services.")
             
 
 ehs_vars <- prep_binary_vars(question, qlabel)
 
 # Plot table of Percentages
 ehs_vars %>% 
   select(Measure = xlab, "Yes (%)" = pct_lab) %>% 
   kable() %>% kable_styling(bootstrap_options = "striped") %>% column_spec(2, width='3.5cm')
```
