---
title: "Eating Habits"
format:
  html:
    anchor-sections: false
---

```{r, include=FALSE}
source("common_code.R")

# Print the next figure number
currentFigure <- 0
NextFigure <- function() {
  # Increment the figure number
  currentFigure <<- currentFigure + 1
  
      # -------- Set figure and section number --------
  paste("Figure 8.", currentFigure, ".", sep = "")
}

# Print the next Table number
currentTable <- 0
NextTable <- function() {
  # Increment the table number
  currentTable <<- currentTable + 1
  
      # -------- Set table and section number --------
  paste("Table 8.", currentTable, ".", sep = "")
}

bns$q77 <- recode(bns$q77, "0 servings per day" = "0 servings", "1-2 servings per day" = "1-2 servings", "3-4 servings per day" = "3-4 servings", "5 or more servings per day" = "5+ servings" )
```


Students were asked to report questions related to their eating habits. This includes cooking habits, access to kitchens, access to storing food, fruit and vegetable intake, sugar sweetened beverage intake, fast food intake, alcohol intake, and confidence in cooking. 

*As a reminder, students had the option to select "Prefer not to answer" for all questions, and these responses were set as missing values. In addition, `r get_count_and_percent(bns$finished, 'FALSE')` students did not finish the survey. The n reporting refers to the total number of non-missing responses while the percent reporting reflects the percent of non-missing responses.*


## Food Access and Eating Behaviors


```{r}

# Reverse factor order for some questions and swap positive wording to negative and vice versa

# bns <- bns %>% mutate_at(c('q76_1', 'q76_3', 'q76_4', 'q76_5', 'q76_6', 'q76_7', 'q76_8', 'q76_9'), fct_rev) %>% mutate_at(c('q76_1', 'q76_3', 'q76_4', 'q76_5', 'q76_6', 'q76_7', 'q76_8', 'q76_9'), recode, "Strongly agree" = "Strongly disagree", "Agree" = "Disagree", "Strongly disagree" = "Strongly agree", "Disagree" = "Agree")


```

```{r}
#| fig-height: 4
#| fig-width: 7.5
questions1 <- bns %>% select(q76_2, q76_4, q76_5, q76_6, q76_8)
names(questions1) <- c("I have a secure place to store fresh food and pantry items.",
                      "Thinking about food is stressful/causes anxiety.",
                      "I wish I had more food to eat.",
                      "I almost always skip meals.",
                      "No one cooks at home.")
plot_likert(questions1,
            grid.range = c(1.5, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")


```

```{r}
#| fig-cap: !expr sprintf("%s Food Access and Eating Behaviors.", NextFigure())
#| fig-height: 4
#| fig-width: 7.5
questions <- bns %>% select(q76_1, q76_3, q76_7, q76_9)
names(questions) <- c("I do not regularly have access to a kitchen where I can prepare meals.",
                      "I do not have enough room to store food items.",
                      "I don't cook or shop for food.",
                      "I do not think about my eating/food habits.")
plot_likert(questions,
            grid.range = c(1.5, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```


**Survey Question:** *For each of the following statements, indicate how strongly you agree or disagree about your current eating and cooking habits:*


**Summary:** Some highlights of the results include the following: A total of `r count_and_percent(bns$q76_1, "Agree", "Strongly agree")` students agreed or strongly agreed that they did not have access to a kitchen; `r count_and_percent(bns$q76_3, "Agree", "Strongly agree")` agreed or strongly agreed that they did not have enough room to store food items; `r count_and_percent(bns$q76_4, "Agree", "Strongly agree")` agreed or strongly agreed that thinking about food was stressful or caused anxiety; and `r count_and_percent(bns$q76_5, "Agree", "Strongly agree")` agreed or strongly agreed that they wished they had more food to eat. 


<br />

## Daily Fruit & Vegetable Intake


```{r}
#| fig-cap: !expr sprintf("%s Daily Fruit & Vegetable Intake %s.", NextFigure(), print_n_reporting("q77"))
#| fig-height: 5
#| fig-width: 6

plot_frq(bns$q77, geom.colors = plot_color) + xlab('Daily Fruit & Vegetable Servings') + ylab("Number of Students")

```


**Survey Question:** [*How many servings of fruits and vegetables do you usually consume per day? (1 serving= 1 medium piece of fruit; 1/2 cup fresh, frozen, or canned fruits/vegetables; 1 cup salad greens; or 1/4 cup dried fruit). Do NOT include fruit juices.^1^*](#Footnotes)


**Summary:** A total of `r get_count_and_percent(bns$q77, "0 servings")` students reported usually eating zero servings of fruits and vegetables per day, `r get_count_and_percent(bns$q77, "1-2 servings")` reported eating one to two servings per day, `r get_count_and_percent(bns$q77, "3-4 servings")` reported eating three to four servings per day, and only `r get_count_and_percent(bns$q77, "5+ servings")` reported eating five or more servings per day.

<br />



## Daily Sugar-Sweetened Beverage Intake


```{r}
#| fig-cap: !expr sprintf("%s Daily Sugar Sweetened Beverage Intake %s.", NextFigure(), print_n_reporting("q78"))
#| fig-height: 5
#| fig-width: 6

bns$q78 <- recode(bns$q78, "Zero" = "Zero",
                   "1-8 ounces" = "1-8", 
                   "9-16 ounces" = "9-16",  
                   "17-24 ounces" =  "17-24", 
                   "25-36 ounces" = "25-36",
                  "37-48 ounces" = "37-48", 
                  "49-56 ounces" =  "49-56", 
                  "57-64 ounces" = "57-64", 
                  "64 ounces or more" = "64+")

plot_frq(bns$q78, geom.colors = plot_color) + xlab('Daily Sugar-Sweetened Beverage Intake (Ounces)') + ylab("Number of Students") 

```

**Survey Question:** *How many ounces of regular soda/cola/pop, sports drinks, energy drinks, or sweetened coffee and tea beverages do you consume each day? Do NOT count diet or zero-calorie drinks. Consider 8 ounces is 1 cup/glass of soda; 1 can of soda is 12 ounces; 1 bottle of juice is typically 16-20 ounces; 2 Liter bottle of soda is 68 oz; 1 Liter sweetened iced tea is 34 oz*


**Summary:** A total of `r get_count_and_percent(bns$q78, "Zero")` students reported drinking zero servings of sugar-sweetened beverages per day, `r get_count_and_percent(bns$q78, "1-8")` reported drinking one to eight ounces per day, and `r get_count_and_percent(bns$q78, "9-16")` reported drinking nine to 16 ounces per day. The remaining `r count_and_percent(bns$q78, "17-24", "25-36", "37-48", "49-56", "57-64", "64+")` students reported drinking 17 or more ounces per day.


<br />

## Weekly Fast Food Intake

```{r}
#| fig-cap: !expr sprintf("%s Weekly Fast Food Intake %s.", NextFigure(), print_n_reporting("q79"))
#| fig-height: 5
#| fig-width: 6

bns$q79 <- recode(bns$q79, "Zero" = "Zero times", 
                   "1-2 times per week" = "1-2 times", 
                   "3-4 times per week" = "3-4 times",
                   "5-6 times per week" = "5-6 times",
                   "7-8 times per week" = "7-8 times", 
                   "9-10 times per week" = "9-10 times", 
                   "11 times or more per week" = "11+ times")

plot_frq(bns$q79, geom.colors = plot_color) + xlab('Weekly Fast Food Intake') + ylab("Number of Students")
```

**Survey Question:** *How frequently do you eat from fast food restaurants, convenience stores, or vending machines for a meal or meal replacement?*

**Summary:** A total of `r get_count_and_percent(bns$q79, "Zero times")` students reported eating fast food zero times per week, `r get_count_and_percent(bns$q79, "1-2 times")` reported eating fast food one to two times per week, `r get_count_and_percent(bns$q79, "3-4 times")` reported eating fast food three to four times, and the remaining `r count_and_percent(bns$q79, "5-6 times", "7-8 times", "9-10 times", "11+ times")` reported eating fast food five or more times per week. 


<br />

## Weekly Alcohol Intake {#Weekly-Alcohol-Intake}


```{r}
#| fig-cap: !expr sprintf("%s Weekly Alcohol Intake %s.", NextFigure(), print_n_reporting("q80"))
#| fig-height: 5
#| fig-width: 6

levels(bns$q80) <- gsub(" per week", "", levels(bns$q80))
bns$q80 <- recode(bns$q80, "Zero" = "Zero days")


plot_frq(bns$q80, geom.colors = plot_color) + xlab('Weekly Alcohol Intake') + ylab("Number of Students")

```

**Survey Question:** [*How often do you consume at least one serving of alcohol? (1 serving= 12 ounces of beer, a 5-ounce glass of wine, or a drink containing 1 shot of liquor or hard alcohol).^2^*](#Footnotes)

**Summary:** A total of `r count_and_percent(bns$q80, "Zero days")` reported drinking alcohol zero times per week, `r count_and_percent(bns$q80, "1-2 days")` reported drinking alcohol one to two days a week, and the remaining `r count_and_percent(bns$q80, "3-4 days", "5-6 days", "Everyday")` reported drinking alcohol three or more days per week. 

<br />

## Alcohol Servings Consumed


```{r}
#| fig-cap: !expr sprintf("%s Alcohol Servings Consumed When Drinking %s.", NextFigure(), print_n_reporting("q81"))
#| fig-height: 5
#| fig-width: 6



plot_frq(bns$q81, geom.colors = plot_color) + xlab('Alcohol Servings Consumed When Drinking') + ylab("Number of Students")

```

**Survey Question:** [*Typically, how many servings of alcohol do you consume when you drink alcohol? (1 serving = 12 ounces of beer, a 5-ounce glass of wine, or a drink containing 1 shot of liquor or hard alcohol).^2^*](#Footnotes)

**Additional Notes:** This question was displayed only to students who reported drinking alcohol one or more times per week (see [Weekly Alcohol Intake](#Weekly-Alcohol-Intake)).


**Summary:** Of the students that reported drinking at least once per week, `r count_and_percent(bns$q81, "Less than 1 serving")` reported drinking less than one serving when they drink, `r count_and_percent(bns$q81, "1-2 servings")` reported drinking one to two servings, `r count_and_percent(bns$q81, "3-4 servings")` reported drinking three to four servings, and `r count_and_percent(bns$q81, "5 or more servings")` reported drinking five or more servings. 



<br />

## Cooking Confidence

```{r}
#| fig-cap: !expr sprintf("%s Cooking Confidence.", NextFigure())
#| fig-width: 8

questions <- bns %>% select(starts_with("q82_"))
names(questions) <- c("How confident are you that you can use the same healthy ingredient in more than one meal?",
                      "How confident are you that you can use basic cooking skills, like cutting fruits and vegetables, measuring out ingredients, or following a recipe?",
                      "How confident are you that you can buy healthy foods for your family on a budget?",
                      "How confident are you that you can cook healthy foods for your family on a budget?")
plot_likert(questions,
            grid.range = c(1.4, 1.0),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```


**Survey Question:** [*The following questions pertain to how comfortable you feel about buying or preparing food:^3^*](#Footnotes)

**Summary:** Overall, the majority of students feel confident in their cooking habits. A notable `r count_and_percent(bns$q82_1, "Not at all confident", "Not very confident", "Neutral")` students were neutral, not very confident, or not at all confident that they can use the same healthy ingredients in more than one meal; `r count_and_percent(bns$q82_2, "Not at all confident", "Not very confident", "Neutral")` were neutral, not very confident, or not at all confident that they can use basic cooking skills; `r count_and_percent(bns$q82_3, "Not at all confident", "Not very confident", "Neutral")` were neutral, not very confident, or not at all confident that they can buy healthy food for their family on a budget; and `r count_and_percent(bns$q82_4, "Not at all confident", "Not very confident", "Neutral")` were neutral, not very confident, or not at all confident that they can cook healthy meals for their family on a budget. 

<br />

--- 

# Footnotes: {#Footnotes}

1. This question was developed from the [Fall 2015-Spring 2019 American College Health Association’s National College Health Assessment](https://www.acha.org/NCHA/About_ACHA_NCHA/Survey/NCHA/About/Survey.aspx?hkey=7e9f6752-2b47-4671-8ce7-ba7a529c9934) which is no longer publicly available.

2. These questions were developed by the [Behavioral Risk Factor Surveillance System](https://www.cdc.gov/brfss/questionnaires/pdf-ques/2018_BRFSS_English_Questionnaire-508.pdf#page=35) screening tool.

3. These questions were developed by the [Share Our Strength’s Cooking Matters survey tool](https://foodsharelc.org/wp-content/uploads/2019/07/2017-Survey.CMF_.English.pdf) (a USDA-SNAP-Ed approved survey).


<br />


:::: {.columns}

::: {.column width="10%"}

:::

::: {.column width="80%"}
<div style="text-align: center;">

<img src="bns_statewide_logo_array.svg" alt="CHC Logo" width="auto" height="auto">

</div>
:::

::: {.column width="10%"}


:::

::::

