---
title: "Website Navigation"
crossref:
  fig-title: 'Figure 1.'
  tbl-title: 'Table 1.'
  fig-labels: arabic
  title-delim: ":"
---

```{r, include=FALSE}
source("common_code.R")
```

-   The website is a tool to present exploratory data analysis results. Results are shown for all campuses combined.
-   Each tab on the header of the website corresponds to a set of questions within the Basic Needs Survey.
-   The top of each page contains a brief paragraph which explains a general overview of questions captured on the page.
-   Within the page, questions were plotted using the most appropriate style for the questions (histogram, barplot, table, etc.). Each graph then has a brief description below it analyzing the results of the graph with the appropriate summary statistics (minimum, mean, max, proportions, etc.).

<br />

## Figure Interpretation

-   Most questions fall under one of the following types of figure styles. Here are some notes on how to interpret them.

### Tables

```{r}
#| label: tbl-exp
#| tbl-cap: Table Caption
data.frame(Questions=c("Question 1 (n = #)", "Question 2 (n = #)", "Question 3 (n = #)"),
           Responses=c("Response # (%)", "Response # (%)", "Response # (%)")) %>%
  kable() %>% kable_styling(bootstrap_options = "striped")
```


-   **Tables** were used to group together sets of questions that typically had a Yes/No response pattern.
-   The left column represents the questions along with the numbers of students who responded to the question.
-   The right column represents the number of student who responded a certain way, along with the percent that responded this way (out of all the students in total that responded).

<br>

### Barplots

```{r}
#| fig-height: 3.2
#| fig-width: 5
#| label: fig-exp1
#| fig-cap: Figure Caption
tmp <- data.frame(q8=bns$q8) %>% mutate(hispanic=as.factor(ifelse(is.na(q8), NA, ifelse(grepl("Yes", q8), "Yes", "No")))) %>% select(-q8)

plot_frq(tmp$hispanic, geom.colors = plot_color, ylim=c(0,1800)) + xlab("x-axis") + ylab("y-axis")
```


-   **Barplots** were used to graph questions which had nominal or ordinal responses (labeled data that's separated into different groups). The x-axis is the response option, and the y-axis is the frequency in which they occured.
-   The numbers above the bars represent the total respondents in the given group, as well as the percent of the data that they comprise.

<br>

### Histograms

```{r}
#| label: fig-exp2
#| fig-cap: Figure Caption
gghistogram(bns, x = "age", add = "mean", alpha = 1, 
            fill = plot_color) + xlab("x-axis") + ylab("y-axis")
```


-   Similar to the barplot above, the **histogram** shows the distribution for a numeric variable of interest on the x-axis and the frequency in which they occured on the y-axis.
-   The mean of the variable of interest is denoted by a vertical dotted line.

<br>

### Likert Plots

```{r}
#| fig-height: 4
#| fig-width: 7
#| label: fig-exp3
#| fig-cap: Figure Caption
questions <- bns %>% select(starts_with("q59_"))
names(questions) <- c("Question 1",
                      "Question 2",
                      "Question 3",
                      "Question 4")
plot_likert(questions,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")

```

-   The **Likert plot** is a barplot visualization for a Likert scale, which is used to measure feelings/opinions for a specific question.\
-   The center line (0%) divides the responses into two groups, such as above where the left side of the chart represents strongly disagree/disagree/neither agree nor disagree and the right hand side represents agree/strongly agree.\
-   The percentages represent the proportion of the data for which the "group" composes.\
-   The (n=#) next to the question denotes how many students responded to a specific question. The values can vary for each question within the same plot.
