---
title: "Basic Needs & Student Success Survey"
subtitle: "UC Berkeley Results"
format:
  html:
    anchor-sections: false
---

```{r, include=FALSE}
source("common_code.R")
library(maps)
library(dplyr)
library(ggplot2)

# # 1) Create Vector of Names of Schools
# Names <- c("UC Berkeley (n = 182)")
# 
# 
# # 2) Set Lat (from Google Maps)
# Lat <- c(37.87032035949273)
# 
# # 3) Set Long (from Google Maps)
# Long <- c(-122.25952497759987)
# 
# # 4) Merge Vectors as data frame
# coord_data <- cbind(Names, Lat, Long) %>% as.data.frame()
# 
# 
# # 5) load California map as data set
# cali_map <- map_data("state") %>% filter(region == "california")
# 
# 
# # 6) Merge California map data and our school data
# map_and_data <- merge(cali_map, coord_data)


```

## Overview

- The [Center for Healthy Communities](https://www.csuchico.edu/chc/) (CHC) developed the **Basic Needs and Student Success Survey (BNS3)** and administered it to undergraduate students participating in the [Educational Opportunity Program (EOP)](https://www2.calstate.edu/attend/student-services/eop) or the Extended Opportunity Programs and Services (EOPS) at 12 colleges across the CSU, CCC, and UC systems from 2022 to 2023.
- This site provides a top level descriptive analysis of each question in the survey for the **UC Berkeley Campus ONLY (n = `r nrow(bns)` students)**
  - [Click here](https://chicocalfresh.github.io/BNS3_Statewide_Summary/) to view the combined results for all 12 campuses.


## Purpose

The main purpose of this third cross-sectional study was to evaluate the following:

- The impact of receiving [CalFresh Food Benefits](https://www.csuchico.edu/calfresh/index.shtml)
- Barriers to applying to CalFresh Food
- College student food insecurity
- The impact of and barriers to using other basic needs services



## Participants

- EOP/EOPS offices assisted in the recruitment by emailing interest form links to their EOP/EOPS students. 
- Students who met the eligibility criteria of being undergraduate EOP/EOPS students and receiving less than 11 meals per week from other services (used as an eligibility criterion when determining CalFresh Food eligibility) were then emailed a survey.
- Participants were given a \$25 gift card incentive for completing the survey. 
- EOP/EOPS students were identified as the target population for this survey based on their low-income and first-generation student status, which indicates a higher probability of using CalFresh Food and being likely eligible for CalFresh Food.
- A total of **`r nrow(bns)` EOP/EOPS students** were surveyed from the UC Berkeley campus.


```{r, fig.width=6, fig.height=4}


# ggplot() + 
#   geom_polygon(data=map_and_data, aes(x=long, y=lat, group=group),
#                 color="black", fill= CF_green) + 
#   geom_point(aes(Long, Lat)) +
#   ggrepel::geom_label_repel(aes(x = Long, 
#                       y = Lat, 
#                       label = Names), nudge_y  = 0.01, min.segment.length = 0) + 
#   theme_void() 

```



**Disclaimer on Missing Data:** *Students had the option to select "Prefer not to answer" for all questions, or options such as "I don't know" for a small subset of questions, and these responses were set as missing values. In addition, `r get_count_and_percent(bns$finished, 'FALSE')` students did not finish the survey. These two factors are the cause of missing data (i.e., not 100% of respondents reporting). In each table/figure, the n reporting refers to the total number of non-missing responses, while the percent reporting reflects the percent of non-missing responses.*

<br />


## Use of Website and Access to Data 

Please reach out to our PI, Stephanie Bianco <span style="color: blue; text-decoration: underline;">sbianco@csuchico.edu</span>, if you would like more information on using or citing this website, accessing the data, methods used, or survey instruments used.




## How to Cite This Website

Center for Healthy Communities. (2023). Statewide Basic Needs and Student Success Survey, UC Berkeley Results. https://chicocalfresh.github.io/BNS3_Statewide_Summary_UC_Berkeley/


## Other Sites

[Statewide Basic Needs and Student Success Survey](https://chicocalfresh.github.io/BNS3_Statewide_Summary/)


<br />

:::: {.columns}

::: {.column width="10%"}

:::

::: {.column width="80%"}
<div style="text-align: center;">

<img src="bns_statewide_logo_array.svg" alt="CHC Logo" width="auto" height="auto">

</div>
:::

::: {.column width="10%"}


:::

::::



