---
title: "Other Basic Needs"
format:
  html:
    anchor-sections: false
---

```{r, include=FALSE}
source("common_code.R")


# Print the next figure number
currentFigure <- 0
NextFigure <- function() {
  # Increment the figure number
  currentFigure <<- currentFigure + 1
  
      # -------- Set figure and section number --------
  paste("Figure 6.", currentFigure, ".", sep = "")
}

# Print the next Table number
currentTable <- 0
NextTable <- function() {
  # Increment the table number
  currentTable <<- currentTable + 1
  
      # -------- Set table and section number --------
  paste("Table 6.", currentTable, ".", sep = "")
}

```


Students were asked to report information relating to their campus food pantry, Medi-Cal, and emergency housing services. Those that have utilized these services were asked to report their perceived impact of these services, while those that were not using them were asked to report any barriers to accessing them. 


*As a reminder, students had the option to select "Prefer not to answer" for all questions, and these responses were set as missing values. In addition, `r get_count_and_percent(bns$finished, 'FALSE')` students did not finish the survey. The n reporting refers to the total number of non-missing responses, while the percent reporting reflects the percent of non-missing responses.*




## Basic Needs {#Basic-Needs}

```{r}
#| fig-cap: !expr sprintf("%s Basic Needs Services Usage.", NextFigure())
#| fig-height: 4
#| fig-width: 8.2
questions <- bns %>% select(q46_2 ,q46_3, q46_4)

questions <-
  questions %>% mutate(across(everything(), function(x)
    fct_relevel(
      x,
      "Never heard of it",
      "Heard of it, but never used it",
      "Used it before attending college",
      "Used it in the past as a college student",
      "Currently use as a college student"
    )))

names(questions) <-
  c(
    'Campus food pantry (e.g., food, toiletries, feminine products)',
    'Medi-Cal',
    'Emergency Housing Services'
  )
plot_likert(
  questions,
  grid.range = c(1.3, 1.3),
  wrap.legend.labels = 20,
  expand.grid = FALSE,
  values = "sum.outside",
  catcount = 5,
  geom.colors = likert.pal.5,
  show.prc.sign = TRUE,
  reverse.scale = TRUE
) + theme_bw() + theme(legend.position = "top")
```


**Survey Question:** *Please mark all the statements that apply to you.*

**Summary:** A total of `r count_and_percent(bns$q46_2, "Currently use as a college student", "Used it in the past as a college student")` students reported currently using their campus food pantry or have used it in the past as a college student compared to `r count_and_percent(bns$q46_3, "Currently use as a college student", "Used it in the past as a college student")` students for Medi-Cal and only `r count_and_percent(bns$q46_4, "Currently use as a college student", "Used it in the past as a college student")` for emergency housing services.




## Food Pantry Usage

```{r}
#| fig-cap: !expr sprintf("%s Food Pantry Usage %s.", NextFigure(), print_n_reporting('q54'))


bns$q54 <- recode(bns$q54, "Other (Please specify):" = "Other")

plot_frq(bns$q54, geom.colors = plot_color, wrap.labels = 12) + 
  xlab('\nHow often do you normally use the food pantry?')+ 
  theme(axis.text=element_text(size=9), #change font size of axis text
        axis.title=element_text(size=9))
```


**Survey Question:** *Indicated in x-axis Labels*

**Additional Notes:** Only students who reported that they *Currently use the campus food pantry as a student,* or *Used it in the past as a college student* saw this question (See [Basic Needs](#Basic-Needs) section).

**Summary:** Of those who reported currently using their campus food pantry or have used it in the past as a college student, `r get_count_and_percent(bns$q54, "Not every week")` students reported using it less than once a week, `r get_count_and_percent(bns$q54, "About once a week")` reported using it about once a week, and `r get_count_and_percent(bns$q54, "More than once a week")` reported using it more than once a week. 


## Food Pantry - Impact

**Because I utilized campus food pantries:**

```{r}
#| fig-height: 8
#| fig-width: 8.5
questions <- bns %>% select(starts_with("q55_"))
names(questions) <- c('I worked fewer hours each week in a PAID position.',
                      'I had more time to do an UNPAID internship or volunteer work.',
                      'I did not worry about whether I would run out of food or whether my food would last each month.',
                      'I had more money to pay for bills (rent, utility bills, clothes, etc.).',
                      'I had more money for entertainment and social activities (e.g. attending movies, shopping, going to bars or parties, etc.)',
                      "I shopped more frequently at the farmers' market.",
                      'I purchased healthier foods.',
                      'I cooked more frequently at home.',
                      'I consumed a healthier diet.',
                      'I consumed less fast food.',
                      'I consumed fewer processed foods.',
                      'I consumed fewer ready-to-eat meals.',
                      'I consumed less junk food.',
                      'I consumed fewer sugar-sweetened beverages like soda and energy drinks.',
                      'I concentrated more in class(es).',
                      'My grades had improved.',
                      'I kept up with course materials, for example reading, writing, and preparing for exams and course assignments.',
                      'I had more time to go to my professors office hours and tutoring services when needed.',
                      'I had more time to attend all my classes',
                      'I had more time to go on field trips or internships.',
                      'My sleep quality had improved.',
                      "My stress/anxiety level had decreased. (eg. I'm not stressed/anxious about having money for food or bills).")
plot_likert(questions[1:11],
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")

```



```{r}
#| fig-cap: !expr sprintf("%s Food Pantry Impact.", NextFigure())
#| fig-height: 8
#| fig-width: 8.5
plot_likert(questions[12:22],
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")

```


**Survey Question:** *For the following questions, please choose how much you agree or disagree with the impact CalFresh has or had on your life. Because I utilized campus food pantries:*


**Additional Notes:** Only students who reported that they *Currently use the campus food pantry as a student,* or *Used it in the past as a college student* saw this question (See [Basic Needs](#Basic-Needs) section).


**Summary:** Some highlights of the results include the following: Because students utilized their campus food pantries, `r count_and_percent(bns$q55_1, "Disagree", "Strongly disagree", "Neither agree nor disagree")` were neutral, disagreed, or strongly disagreed that they worked fewer hours in a paid position each week; and `r count_and_percent(bns$q55_6, "Disagree", "Strongly disagree", "Neither agree nor disagree")` were neutral, disagreed, or strongly disagreed that they shopped more frequently at the farmers' market. Meanwhile, `r get_count_and_percent2(bns$q55_8, "Agree", "Strongly agree")` students agreed or strongly agreed that they cooked more frequently at home; and  `r get_count_and_percent2(bns$q55_3, "Agree", "Strongly agree")` agreed or strongly agreed that they did not worry about food running out each month because of the food pantry. 


<br>




## Food Pantry - Barriers

```{r}
#| tbl-cap: !expr sprintf("%s Food Pantry Barriers %s.", NextTable(), print_n_reporting('no_pantry_dont_need'))


 question <- "no_pantry"
 qlabel <- c("My family doesn't want me to go to campus food pantries or local food banks.",
             'I am embarrassed or scared to go to the campus food pantries or local food banks.',
             'I do not believe in using campus food pantries or local food banks.',
             "Inconvenient to access due to lack of transportation or out-of-the way location.",
             'Inconvenient times of operation/limited pantry hours.',
             'I feel other students need the food more than I do.',
             'I am not aware of any campus food pantries or local food banks.',
             'There are no food pantries close to campus or my residence.',
             'Other', 
             "I don't need to use campus food pantries.", 
             'I feel uncomfortable about receiving help with basic needs, like food.',
             'I would think less of myself If I went to campus food pantries or local food banks.',
             "I don't want my friends to find out I go to campus food pantries or local food banks.",
             'My friends and peers would think less of me if I went to food pantries or local food banks.')
 
 pantry_vars <- prep_binary_vars(question, qlabel)

# Plot table of Percentages
 pantry_vars %>% 
   select("Reasons for Not Using Campus Food Pantries:" = xlab, "Yes (%)" = pct_lab) %>% 
   kable() %>% kable_styling(bootstrap_options = "striped")
```


**Survey Question:** *What are the reasons you do not go to campus food pantries? (Select all that apply)*

**Additional Notes:** Only students who reported that they *Never heard of the campus food pantry;* *Heard of it, but never used it;* or *Used it before attending college* saw this question (See [Basic Needs](#Basic-Needs) section).


**Summary:** The most common reason students reported not using their campus food pantry was because they felt that other students need the food more than them, where `r get_count_and_percent(bns$no_pantry_other_students_need, "1")` students selected this option. Meanwhile, `r get_count_and_percent(bns$no_pantry_dont_need, "1")` reported they did not need to use the food pantry, and `r get_count_and_percent(bns$no_pantry_not_aware, "1")` reported they were not aware of any campus food pantries or local food banks. Please note, some campuses may not have food pantries on or near their campus. 

<br>


## Medi-Cal - Impact

**Knowing that I have Medi-Cal:**

```{r}
#| fig-cap: !expr sprintf("%s Medi-Cal Impact.", NextFigure())
#| fig-width: 8.5
questions <- bns %>% select(starts_with("q59_"))
names(questions) <- c("My mental health has improved.",
                      "My physical health has improved.",
                      "My sleep quality had improved.",
                      "My stress/anxiety level had decreased. (ex. I’m not stressed/anxious about having money for food or bills).")
                      

plot_likert(questions,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```


**Survey Question:** *For the following questions, please choose how much you agree or disagree with the impact Medi-Cal has or had on your life. Knowing that I have Medi-Cal:*

**Additional Notes:** Only students who reported that they *Currently use Medi-Cal as a student,* or *Used it in the past as a college student* saw this question (See [Basic Needs](#Basic-Needs)).

**Summary:** Because students used Medi-Cal, `r count_and_percent(bns$q59_1, "Disagree", "Strongly disagree", "Neither agree nor disagree")` were neutral, disagreed, or strongly disagreed that their mental health has improved; `r get_count_and_percent2(bns$q59_2, "Agree", "Strongly agree")` agreed or strongly agreed that their physical health had improved; `r count_and_percent(bns$q59_3, "Disagree", "Strongly disagree", "Neither agree nor disagree")` were neutral, disagreed, or strongly disagreed that their sleep quality had improved; and `r count_and_percent(bns$q59_4, "Disagree", "Strongly disagree", "Neither agree nor disagree")` were neutral, disagreed, or strongly disagreed that their stress/anxiety level had decreased. 





<br>

## Medi-Cal - Barriers


```{r}
#| tbl-cap: !expr sprintf("%s Medi-Cal Barriers %s.", NextTable(), print_n_reporting('no_medical_dont_need'))

 question <- "no_medical"
 qlabel <- c("I don’t need Medi-Cal.",
             "I do not know what Medi-Cal is or I think I already have health insurance.",
             "I only need medical services at the student health center associated with my campus.",
             "No time to complete the Medi-Cal application/Medi-Cal application is too long.",
             "The Medi-Cal application is too difficult to complete.",
             "I do not think I am eligible for Medi-Cal.",
             "I have heard from other students that it is not worth my time because I wont be eligible.",
             "My family or household does not want me to apply for Medi-Cal.",
             "I am embarrassed or ashamed to apply for Medi-Cal.",
             "I don’t believe in social services like Medi-Cal, CalFresh, WIC, or Welfare/Cash Aid.",
             "Other",
             "I feel uncomfortable about receiving help with basic needs, like medical care.",
             "I would think less of myself If I applied for Medi-Cal.",
             "I don't want my friends to find out I applied for Medi-Cal.",
             "My friends and peers would think less of me if I applied to Medi-Cal.")
 
 medical_vars <- prep_binary_vars(question, qlabel)
 
 # Plot table of Percentages
 medical_vars %>% 
   select("Reasons for Not Using Medi-Cal:" = xlab, "Yes (%)" = pct_lab) %>% 
   kable() %>% kable_styling(bootstrap_options = "striped")
```


**Survey Question:** *What are the reasons you do not have Medi-Cal or have never used Medi-Cal? (Select all that apply).*

**Additional Notes:** Only students who reported that they *Never heard of Medi-Cal; Heard of it, but never used it; or Used it before attending college* saw this question (See [Basic Needs](#Basic-Needs) section).

**Summary:** A total of `r get_count_and_percent(bns$no_medical_unknown, "1")` students did not use Medi-Cal because they did not know what Medi-Cal was or they already had another health insurance. Meanwhile, `r get_count_and_percent(bns$no_medical_dont_need, "1")` reported not needing Medi-Cal, and `r get_count_and_percent(bns$no_medical_eligible, "1")` did not think they were eligible.



<br>

## Emergency Housing Services - Impact

**Because I received Emergency Housing Services:**

```{r}
#| fig-cap: !expr sprintf("%s Emergency Housing Services Impact.", NextFigure())
#| fig-height: 8
#| fig-width: 8.5
questions <- bns %>% select(starts_with("q62_"))
names(questions) <- c('I concentrated more in class(es).',
                      'My grades had improved.',
                      'I kept up with course materials, for example reading, writing, and preparing for exams and course assignments.',
                      'I had more time to go to my professors’ office hours and tutoring services when needed.',
                      'I had more time to attend all my classes',
                      'I had more time to go on field trips or internships.',
                      'My sleep quality had improved.',
                      'My stress/anxiety level had decreased. (ex. I’m not stressed/anxious about having money for food or bills).',
                      'I’m less concerned about housing issues.',
                      'I felt more confident in my ability to maintain healthy relationships.')

plot_likert(questions,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

**Survey Question:** *For the following questions, please choose how much you agree or disagree with the impact Emergency Housing Services have or had on your life. Because I received Emergency Housing Services:*


**Additional Notes:** Only students who reported that they *Currently use Emergency Housing Services as a student,* or *Used it in the past as a college student* saw this question (See [Basic Needs](#Basic-Needs) section).

**Summary:** Some highlights of the results include the following: Because students utilized emergency housing services, `r get_count_and_percent2(bns$q62_1, "Agree", "Strongly agree")` agreed or strongly agreed that they concentrated more in class; `r get_count_and_percent2(bns$q62_2, "Agree", "Strongly agree")` agreed or strongly agreed that their grades had improved; `r get_count_and_percent2(bns$q62_8, "Agree", "Strongly agree")` agreed or strongly agreed that their stress/anxiety had decreased; and `r get_count_and_percent2(bns$q62_9, "Agree", "Strongly agree")` agreed or strongly agreed that they were less concerned about housing issues. 





<br>

## Emergency Housing Services - Barriers


```{r}
#| tbl-cap: !expr sprintf("%s Emergency Housing Services Barriers %s.", NextTable(), print_n_reporting('no_ehs_dont_need'))

 question <- "no_ehs"
 qlabel <- c("I don’t need Emergency Housing Services",
             "I was not aware that my campus had Emergency Housing Services like grants and housing placements in an emergency.",
             "No time to complete the Emergency Housing application or contact the Emergency Housing Staff.",
             "The Emergency Housing Services application is too difficult to complete.",
             "The emergency housing grant/money is not enough to support what I need, so not worth my time to apply for it.",
             "I am embarrassed or ashamed to apply for Emergency Housing Services.",
             "I do not believe in social services like Emergency Housing Services, Medi-Cal, CalFresh, or Welfare/Cash Aid.",
             "Other", 
             "I feel uncomfortable about receiving help with basic needs, like housing.",
             "I would think less of myself if I applied for Emergency Housing Services.",
             "I don't want my friends to find out that I applied for emergency housing services.",
             "My friends and peers would think less of me if I applied for emergency housing services.")
             
 
 ehs_vars <- prep_binary_vars(question, qlabel)
 
 # Plot table of Percentages
 ehs_vars %>% 
   select("Reasons for Not Using Emergency Housing Services:" = xlab, "Yes (%)" = pct_lab) %>% 
   kable() %>% kable_styling(bootstrap_options = "striped") %>% column_spec(2, width='3.5cm')
```



**Survey Question:** *What are the reasons you do not use Emergency Housing Services or have never used Emergency Housing Services? (Select all that apply)*

**Additional Notes:** Only students who reported that they *Never heard of Emergency Housing Services; Heard of it, but never used it; or Used it before attending college* saw this question (See [Basic Needs](#Basic-Needs) section).

**Summary:** A total of `r get_count_and_percent(bns$no_ehs_dont_need, "1")` students did not use Emergency Housing Services because they reported not needing them, while `r get_count_and_percent(bns$no_ehs_not_aware, "1")` did not know that their campus offered emergency housing services. Please note, some campuses may not offer emergency housing services. 



<br />

:::: {.columns}

::: {.column width="10%"}

:::

::: {.column width="80%"}
<div style="text-align: center;">

<img src="bns_statewide_logo_array.svg" alt="CHC Logo" width="auto" height="auto">

</div>
:::

::: {.column width="10%"}


:::

::::




