---
title: "Physical Activity"
format:
  html:
    anchor-sections: false
---

```{r, include=FALSE}
source("common_code.R")

# Print the next figure number
currentFigure <- 0
NextFigure <- function() {
  # Increment the figure number
  currentFigure <<- currentFigure + 1
  
      # -------- Set figure and section number --------
  paste("Figure 9.", currentFigure, ".", sep = "")
}

# Print the next Table number
currentTable <- 0
NextTable <- function() {
  # Increment the table number
  currentTable <<- currentTable + 1
  
      # -------- Set table and section number --------
  paste("Table 9.", currentTable, ".", sep = "")
}

```

Students were asked to select how many days in the last week they had done any of the following exercise types: [moderate, vigorous, or strength training exercises.^1^](#Footnotes)

*As a reminder, students had the option to select "Prefer not to answer" for all questions, and these responses were set as missing values. In addition, `r get_count_and_percent(bns$finished, 'FALSE')` students did not finish the survey. The n reporting refers to the total number of non-missing responses, while the percent reporting reflects the percent of non-missing responses.*


## Physical Activity Type {#Physical-Activity-Type}

```{r, results='asis'}
#| tbl-cap: !expr sprintf("%s Physical Activity Patterns.", NextTable())


tmp <- data.frame(rbind(table(bns$q83_1),
                        table(bns$q83_2),
                        table(bns$q83_3)))

tmp <- as.data.frame(apply(tmp, 1, function(x) paste0(x, " (", percent(x/sum(x), accuracy = 0.1), ")")))
colnames(tmp) <- c("Moderate Exercise", "Strength Training", "Vigorous Training")
tmp["Days"] <- 0:7
tmp <- tmp[c(4,1,2,3)]
tmp <- t(tmp)

tmp %>%
  kable() %>% kable_styling(latex_options = c("HOLD_position", "striped", "bordered", "hover"))  %>%  
    row_spec(1, bold = T, color = "white", background = CF_green) 


```



```{r, fig.width=8}
#| fig-cap: !expr sprintf("%s Physical Activity Patterns.", NextFigure())



tmp1 <- cbind(data.frame(Question=rep("Moderate Exercise", 8)), as.data.frame(table(bns[["q83_1"]])))
tmp2 <- cbind(data.frame(Question=rep("Vigorous Exercise", 8)), as.data.frame(table(bns[["q83_2"]])))
tmp3 <- cbind(data.frame(Question=rep("Strength Training", 8)), as.data.frame(table(bns[["q83_3"]])))
pa.data <- rbind(tmp1, tmp2, tmp3)
colnames(pa.data) <- c('Type', 'Days', 'Freq')
rm(tmp1, tmp2, tmp3)

ggplot(pa.data) +
    geom_linerange(aes(x = Days, ymin = 0, ymax = Freq, colour = Type), 
                   position = position_dodge(width = 0.6), size=1) +
    geom_point(aes(x = Days, y = Freq, colour = Type),
               position = position_dodge(width = 0.6), size=2.5) + scale_color_manual(values=c("#336699", "#000000", "#b5d43b")) +
  labs(colour='Exercise Type') + xlab('Number of Days') + ylab('Number of Students') + theme_bw() +
  theme(legend.key.size = unit(1, 'cm'), 
        legend.key.height = unit(1, 'cm'), 
        legend.key.width = unit(1, 'cm'), 
        legend.title = element_text(size=13),
        legend.text = element_text(size=11))


```


**Survey Questions:** *On how many of the past 7 days did you: (Please mark the appropriate column for each row)*

- *Do moderate-intensity cardio or aerobic exercise (caused a noticeable increase in heart rate, such as brisk walk) for at least 30 minutes?* `r print_n_reporting("q83_1")`

- *How often did you do 8-10 strength training exercises (such as resistance weight machines) for at least 8 repetitions each?* `r print_n_reporting("q83_3")`

- *How often did you do vigorous-intensity cardio or aerobic exercise (caused large increases in breathing or heart rate, such as jogging) for at least 20 minutes?* `r print_n_reporting("q83_3")`



**Additional Notes:** For each exercise type, students had the option to select anywhere from zero days per week to seven days per week. In the table, percentages are calculated across rows. 

**Summary:** The majority of students reported doing moderate-intensity exercises at least once in the past seven days, and `r get_count_and_percent(bns$q83_1, "0 days")` reported doing this zero times. About half the students reported doing strength training exercises at least once in the past 7 days, and `r get_count_and_percent(bns$q83_2, "0 days")` reported doing this zero times. Less than half of the students reported doing vigorous-intensity cardio or aerobic exercises at least once in the past 7 days, and `r get_count_and_percent(bns$q83_3, "0 days")` reported doing this zero times. 



<br />


## Weekly Physical Activity 

```{r}
#| fig-cap: !expr sprintf("%s Weekly Physical Activity %s", NextFigure(), print_n_reporting("physical_activity"))
#| fig-height: 4
#| fig-width: 5


# Physical activity indicator

bns <- bns %>% mutate_at(c('q83_1', 'q83_2', 'q83_3'), recode,
                         "0 days" = 0, "1 day" = 1, "2 days" = 2, "3 days" = 3, "4 days" = 4, "5 days" = 5, "6 days" = 6, "7 days" = 7)

physical_act_temp <- bns %>% select(q83_1, q83_2, q83_3) %>% rowSums()


bns$physical_activity <- ifelse(physical_act_temp >= 1, "Yes", "No")


# CHeck
# bns %>% select(physical_activity, q83_1, q83_2, q83_3) %>% cbind()


plot_frq(bns$physical_activity, geom.colors = plot_color) + xlab('Weekly Physical Activity') + ylab("Number of Students") + ylim(0, 1.2*max(table(bns$physical_activity)))

```

**Survey Questions:** *See Questions Above*


**Additional Notes:** This variable was created using the variables in the [Physical Activity Type](#Physical-Activity-Type) section. Anyone who performed any type of weekly physical activity (moderate-intensity, strength training, or vigorous-intensity) for one or more days was set to "Yes," and anyone who performed no physical activity per week was set to "No."

**Summary:** A total of `r count_and_percent(bns$physical_activity, "Yes")` students performed any type of physical activity at least once per week, while `r count_and_percent(bns$physical_activity, "No")` performed no weekly physical activity. 

<br />

--- 

# Footnotes: {#Footnotes}

1. These questions were developed based on the [Surgeon General's physical activity guidelines for adults](https://health.gov/sites/default/files/2019-09/Physical_Activity_Guidelines_2nd_edition.pdf) who recommend: 150 minutes to 300 minutes a week of moderate-intensity exercise, 75 minutes to 150 minutes a week of vigorous-intensity aerobic exercise, or an equivalent combination of moderate- and vigorous-intensity aerobic activity. They also recommend strength-training activities on 2 or more days a week.

<br />

:::: {.columns}

::: {.column width="10%"}

:::

::: {.column width="80%"}
<div style="text-align: center;">

<img src="bns_statewide_logo_array.svg" alt="CHC Logo" width="auto" height="auto">

</div>
:::

::: {.column width="10%"}


:::

::::




